Estimating duration in the presence of misclassification

### 2024-03-30 cis-imperfect-testing.tex
fix ref
Modify notation definitions

To formalise this, define the relevant testing times for episode $j$ as $\sched'_j = \{ t \in \sched_{i(j)} \ssep r_j^{(b)} \leq t \leq r_j^{(e)} + 1 \}$ and let $m_j$ denote the size of this set.
Denote the elements of $\sched'_j$ by $t_{j,1} < \dots < t_{j,m_j}$.
The new observation vector for $j$ is $O'(j) = [O(j), \vec{y}_j]^T$ where $\vec{y}_j \in \{ 0, 1 \}^{m_j}$, with $y_{j,l}$ being the test result at time $t_{j,l}$.

Defining analogous variables to \cref{E-perf-test}, let $\set{D}' = \{ \vec{\nu}'_1, \dots, \vec{\nu}'_{N_{D'}} \}$ where $\vec{\nu}'_k \in \set{D}'_k$ if and only if $\vec{\nu}'_k = [\vec{\nu}_k, \vec{y}_k]^T$ would be a detected observation, equivalent to satisfying all the following conditions.
\begin{enumerate}
  \item $\vec{\nu}_k \in \set{D}$.
  \item The elements of $\vec{y}_k$ corresponding to the tests at times $r_k^{(b)}$ (its first element) and $l_k^{(e)}$ (its penultimate element) are 1.
  \item The element of $\vec{y}_k$ corresponding to the test at time $r_k^{(e)} + 1$ (its last element) is 0.
\end{enumerate}
The final two conditions are due the construction of the intervals as positive and negative tests bounding the beginning and end times of the episode.

Similarly, let $p_k'$, $p_{ik}'$, $p_u$, and $p_{iu}$ have the same definition as $p_k$, $p_{ik}$, $p_u$, and $p_{iu}$ respectively except replacing $O$ with $O'$ and $\vec{\nu}_k$ with $\vec{\nu}_k'$, and conditioning on $\psens$.
As before, $p'_k = 1/\Ncis p'_{ik}$ and $p'_u = 1/\Ncis \sum_{i=1}^{\Ncis} p'_{iu}$.

@@

I will modify $p_{ik}$ to form $p_{ik}' = \prob(O'(j) = \nu'_k \mid i(j) = i_k, \vec{\theta})$, taking into account false negatives.
I consider a mixture of two scenarios, whether the final test in $\sched'_{i(j)}$ is a false positive, with the mixture probability determined by the test sensitivity.

>>>>

To formalise this, I define analogous variables to those in \cref{E-perf-test:sec:posterior}.
To start with, define the relevant testing times for episodes with observations $\vec{\nu}_k$ as $\sched'_k = \{ t \in \sched_{i_k} \ssep r_k^{(b)} \leq t \leq r_k^{(e)} + 1 \}$ and let $m_k$ denote the size of this set.
Denote the elements of $\sched'_k$ by $t_{k,1} < \dots < t_{k,m_k}$.
Let $\set{E}' = \{ \vec{\nu}_1', \dots, \vec{\nu}_{N_E'}' \}$ be a new set of possible observations of detected episodes, including the pattern of positive and negative tests.
Represent the observations such that for any $\vec{\nu}_k' \in \set{E}'$, $\vec{\nu}_k' = [\vec{\nu}_{k}, \vec{y}_k]^T$, where $\vec{y}_j \in \{ 0, 1 \}^{m_j}$ with $y_{j,l}$ being the test result at time $t_{j,l}$.

$\vec{\nu}'_k \in \set{E}'$ occurs if and only if all the following conditions are met.
\begin{enumerate}
  \item $\vec{\nu}_k \in \set{E}$.
  \item The elements of $\vec{y}_k$ corresponding to the tests at times $r_k^{(b)}$ and $l_k^{(e)}$ are positive, \ie $y_{k,1} = y_{k,m_k-1} = 1$.
  \item The element of $\vec{y}_k$ corresponding to the test at time $r_k^{(e)} + 1$ is negative, \ie $y_{k,m_k} = 0$.
\end{enumerate}
The final two conditions are due the construction of the intervals as positive and negative tests bounding the beginning and end times of the episode.

Let $O'(j)$ be the observations generated by episode $j$ including the new vector of results.
As before, $O'(j) \in \set{E}'$ indicates that episode $j$ was detected; otherwise, $O'(j) = \emptyset$.

Similarly, let $p_k'$, $p_{ik}'$, $p_u'$, and $p_{iu}'$ have the same definition as $p_k$, $p_{ik}$, $p_u$, and $p_{iu}$ respectively except replacing $O$ with $O'$ and $\vec{\nu}_k$ with $\vec{\nu}_k'$, and conditioning on $\psens$.
As before, $p'_k = 1/\Ncis p'_{ik}$ and $p'_u = 1/\Ncis \sum_{i=1}^{\Ncis} p'_{iu}$.

@@

I will modify $p_{ik}$ to form $p_{ik}' = \prob(O'(j) = \vec{\nu}'_k \mid i(j) = i_k, \vec{\theta})$, taking into account false negatives.
I consider a mixture of two scenarios, whether the final test in $\sched'_{i(j)}$ is a false positive, with the mixture probability determined by the test sensitivity.

### 2024-03-30 incidence-prevalence.tex
Modify notation definitions

\chapter{Data generating process} \label{inc-prev}

@@

Since $D_i$ is a discrete random variable, $0 \leq f_D(d) \leq 1$ for all $d$ and $\sum_{k=1}^{\dmax} f_D(k) = 1$.
By definition, $F_D(d) \in [0, 1]$ and increases monotonically.
Therefore, $S(d) \in [0, 1]$ and decreases monotonically.
Similarly, $\lambda(d) \in [0,1]$, but can otherwise vary arbitrarily (\ie there is no monotonic or sum constraint).
The lack of monotonicity or sum constraint on the hazard makes it an attractive parameterization for inference~\autocite{heBayesian}.

>>>>

\chapter{Data generating processes} \label{inc-prev}

@@

Since $D_i$ is a discrete random variable, $0 \leq f_D(d) \leq 1$ for all $d$ and $\sum_{k=1}^{\dmax} f_D(k) = 1$.
By definition, $F_D(d) \in [0, 1]$ and increases monotonically.
Therefore, $S(d) \in [0, 1]$ and decreases monotonically.
Similarly, $\lambda(d) \in [0,1]$, but can otherwise vary arbitrarily (\ie there is no monotonic or sum constraint).
The lack of monotonicity or sum constraint on the hazard makes it an attractive parameterization for inference because these constraints are challenging to implement in many inference frameworks~\autocite{heBayesian}.
